Interpretable Machine Learning

### 2017-11-15 talk.Rmd
add thoughts on data example

## Predicting house prices
TODO: Add example dataset

>>>>

## Predicting data scientist salaries
Kaggle survey data
n  = ...
Questions asked: ...

## Predicting data scientist scenario
TODO: Show code to fit the model

## Hypothetical scenario
We are an HR consulting company that want to use the model to suggest data scientist compensations for companies. 
We have the model now. 
Do we use it?
